Automated Formal Verification of Stand-alone Solar Photovoltaic Systems

### 2019-07-16 Tex/elsevier/trindade_solar_energy_rev1.tex
fixed typos
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\textcolor{red}{Note that in this study, our focus is not on a novel mathematical modelling of PV systems. Instead, our novelty relies on an effective approach to perform validation of PV systems using software model checking, in a process that is intended to be done just after the system sizing, prior to buying equipment and deploying it in the field, as a safe approach to ensure the intended behavior.}

@@

The most popular softwares are summarized at Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\citep{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.

@@

\noindent where $I_{ph}$ is the photocurrent delivered by the constant current source; $I_{0}$ is the reverse saturation current corresponding to the diode; $N$ is the number of series-connected cells; %($N=1$ in a single cell configuration); 
$a$ is the ideality or quality factor ($a=1$ for ideal diodes and between $1$ and $2$ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}\:J/K $); $T$ the temperature of cell in Kelvin; $q$ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}\:C $).

@@

The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C programs~\citep{esbmc2018}, which supports the verification of LTL properties with bounded traces~\citep{DBLP:journals/sosym/MorseCN015}. ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) preprocessing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability. ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\citep{Morse2015}. This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally. This technique is called ``incremental SMT''~\citep{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.

@@

We have considered five case studies, ranging from \textcolor{red}{$253$ W to $814$ W}; three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker); and one specialized simulation tool (HOMER Pro). The experimental results from automated verification and simulation tools were compared with information collected from dwelles of the sites, where the real PV systems were deployed.} Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool. In particular, the proposed method was successful in finding sizing errors and indicating in details. Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2 GB when compared to 9.2 GB of CBMC and 19.2 GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.

>>>>

\textcolor{red}{Note that in this study, our focus is not on a novel mathematical modeling of PV systems. Instead, our novelty relies on an effective approach to perform validation of PV systems using software model checking, in a process that is intended to be done just after the system sizing, prior to buying equipment and deploying it in the field, as a safe approach to ensure the intended behavior.}

@@

The most popular software tools are summarized in Table~\ref{table:softwares}: PVWatts, SAM, HOMER, RETScreen, and Hybrid2~\citep{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}.

@@

\noindent where $I_{ph}$ is the photo-current delivered by the constant current source; $I_{0}$ is the reverse saturation current corresponding to the diode; $N$ is the number of series-connected cells; %($N=1$ in a single cell configuration); 
$a$ is the ideality or quality factor ($a=1$ for ideal diodes and between $1$ and $2$ for real diodes); $V_{T}$ is the thermal voltage ($ V_{T}=k_{B}T/q $); $ k_{B} $ is the Boltzmann constant ($ 1.3806503\times10^{-23}\:J/K $); $T$ the temperature of cell in Kelvin; $q$ is absolute value of the electron's charge ($ -1.60217646\times10^{-19}\:C $).

@@

The Efficient SMT-based Bounded Model Checker (ESBMC) is a bounded and unbounded model checker for C programs~\citep{esbmc2018}, which supports the verification of Linear-time Temporal Logic (LTL) properties with bounded traces~\citep{DBLP:journals/sosym/MorseCN015}. ESBMC's verification flow can be summarized in three stages: (i) a front-end that can read and compile C code, where the system formal specification is first handled; (ii) pre-processing steps to deal with code representation, control flow and unwinding of loops, and model simplification, thereby aiming to reduce verification effort; and finally (iii) the SMT solving stage, where all constraints and properties of the system are encoded into SMT and checked for satisfiability. ESBMC exploits the standardized input language of SMT solvers (SMT-LIB\footnote{http://smtlib.cs.uiowa.edu/} logic format) to make use of a resource called \textit{assertion stack}~\citep{Morse2015}. This enables ESBMC, and the respective solver, to learn from previous checks, thus optimizing the search procedure and potentially eliminating a large amount of formula state space to be searched, because it solves and disregards data during the process, incrementally. This technique is called ``incremental SMT''~\citep{DBLP:journals/fac/SchrammelKBMTB17} and allows ESBMC to reduce the memory overhead, mainly when the verified system is complex and the computing platform does not have large amount of memory to deal with the entire design space state.

@@

We have considered five case studies, ranging from \textcolor{red}{$253$ W to $814$ W}; three state-of-art verification engines were considered (ESBMC, CBMC, and CPAchecker); and one specialized simulation tool (HOMER Pro). The experimental results from automated verification and simulation tools were compared with information collected from dwellers of the sites, where the real PV systems were deployed.} Although the verification method proposed takes longer than simulation methods, it is able to present details that lead to failures in a PV system that is not a feature presented in commercial simulation tool. In particular, the proposed method was successful in finding sizing errors and indicating in details. Related to the verification engines comparative, the ESBMC with the Z3 solver executed in the incremental configuration presented the better performance (around four times faster than CBMC), used less RAM memory (less than 2 GB when compared to 9.2 GB of CBMC and 19.2 GB of CPAchecker), and all the results were sound because the PV owners and the monitoring system validated the possible flaws that the system could be presenting in the field.
